Rapid response of mesophyll conductance to light availability allows shade leaves to take advantage of sunflecks

### 2015-12-07 manuscript/manuscript_wtc3.Rmd
figure caption edit

\
**Figure S4**. Response of VPD (a), g~s~ (b) and C~a~-C~i~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represents each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Leaf VPD inside the gas exchange cuvette was positively correlated with increasing leaf temperature for sun leaves and shade leaves at low and high light (R^2^ = 0.73, 0.58 and 0.72, respectively)

>>>>

\
**Figure S4**. Response of VPD (a), g~s~ (b) and C~a~-C~i~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represents each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Leaf VPD inside the gas exchange cuvette was positively correlated with increasing leaf temperature for sun leaves and shade leaves at low and high light (R^2^ = 0.73, 0.58 and 0.72, respectively).
